\vspace{24pt} In-Memory Trajectory Analysis on Taxi Data

### 2018-08-21 paper/paper.tex
motivation

\section{Data Sources}

@@

>>>>

Traditional taxi companies like to increase their profit. For that, the individual taxi drivers would have to find many passengers and minimize their waiting times. A way to be a  good performing taxi is to stay in a profitable area of the city. For example, where taxi rides are highly needed at a specific time. With our help, the taxi companies can develop new strategies. A simple strategy would be to only accept and assign orders whose destination is in a good area for the expected arrival time. We created an interactive map, which shows the best performing taxis for one day in Shenzhen. This is based on a data set that is explained in section \ref{sec:ds}. The application has some additional information about the taxi density and numbers about pick-ups and drop-offs. Taxi companies could use the application to quickly analyze the collected GPS data.

\section{Data Sources}
\label{sec:ds}

@@

% mehr daten hinzufuegen. kein problem, da alle queries optimiert wurden
